\section*{Technical Presentations}

\subsection*{Conferences}

\begin{itemize}
    \item ``Mesoscale Simulations Investigating the Effects of Shock Wave Stability in Granular Materials with Peridynamics.'' (with R.~Rahman, A.~Peterson, T.~Vogler). 13th US National Congress on Computational Mechanics. July 2015.
    \item ``Regularizing numerical simulations of shear-banding using a peridynamics-based plasticity formulation.'' (with Md.I.H.~Kahn). ASME 2014 International Mechanical Engineering Congress and Exposition. November 2014.
    \item ``An Ordinary State Based Plasticity Model For Peridynamics.'' (with J.A.~Mitchell). ASME 2014 International Mechanical Engineering Congress and Exposition. November 2014.
    \item ``Fracture in plates and shells with peridynamic non-ordinary state-based models.''  Meshfree Methods for Large-Scale Computational Science and Engineering. October 2014.
    \item ``An Overview of the Progress of Meshfree Particle Methods: From SPH to EFG to RKPM to Meshfree Peridynamics.'' (with W.K~Liu, M.~Bessa). Meshfree Methods for Large-Scale Computational Science and Engineering. October 2014.
    \item ``A nonlocal poroelastic approach to fluid driven fracture.'' (with J.~York, A.~Katiyar, H.~Ouchi, M.~Sharma). World Congress on Computational Mechanics XI.  July 2014.
    \item ``Reproducing Continuum Dynamics''. (with M.~Bessa, W.K.~Liu, T.~Belytschko). World Congress on Computational Mechanics 2014.  July 2014.
    \item ``A nonlocal poroelastic approach to fluid driven fracture.'' (with J.~York, A.~Katiyar, H.~Ouchi, M.~Sharma). US National Congress on Theoretical and Applied Mechanics.  June 2014.
    \item ``Bridging the length scales by linking the atomistic model with coarser peridynamic models through molecular dynamics simulation of Polyethylene''. (with R.~Rahman). Mach Conference 2014.  April 2014.
    \item ``Regularizing numerical simulations of strain-localization using a peridynamics-based plasticity formulation''. (with Md.I.~Kahn, D.J.~Littlewood, and J.A.~Mitchell). International Workshop on Computational Mechanics of Materials, IWCMM XXIII. October 2013
    \item ``A non-local formulation for fluid flow and mass transport in porous media based on peridynamic theory''. (with A.~Katiyar and M.~Sharma). 12th US National Congress on Computational Mechanics. July 2013.
    \item ``A novel hierarchical multiscale modeling framework for polyethylene systems using Peridynamics and molecular dynamics''. (with R. Rahman). 2013 Mach Conference, Annapolis, MD. April 2013. 
    \item ``Two-Dimensional Semi-Analytic Solutions to the Linearized State-Based Peridynamic Equilibrium Equation''. (with J.T. O'Grady). USACM Workshop on Nonlocal Damage and Failure: Peridynamics and other nonlocal methods. March 2013.
    \item ``A Peridynamics Based Hierarchical Multiscale Modeling Framework Between Continuum and Atomistic Scales''. (with R. Rahman, A. Haque). USACM Workshop on Nonlocal Damage and Failure: Peridynamics and other nonlocal methods. March 2013.
    \item ``Lessons Learned in Modeling Ductile Failure with Peridynamics''. (with D.J. Littlewood). USACM Workshop on Nonlocal Damage and Failure: Peridynamics and other nonlocal methods. March 2013.
    \item ``A Peridynamics Formulation of the Coupled Mechanics-Fluid Flow Problem''. (with A. Katiyar, H. Ouchi, M.M. Sharma). USACM Workshop on Nonlocal Damage and Failure: Peridynamics and other nonlocal methods. March 2013.
    \item ``Implicit time integration of an ordinary state-based peridynamic plasticity model with isotropic hardening.'' (with D.J. Littlewood, J.A. Mitchell, M.L. Parks).  ASME IMECE 2012.  November 2012.
    \item ``Implicit time integration of an ordinary state-based peridynamic plasticity model with isotropic hardening.'' (with D.J. Littlewood, J.A. Mitchell, M.L. Parks).  SiViRT Simulation and Vizualization Symposium.  November 2012.
    \item ``Peridynamic Modeling of Localization in Ductile Metals.'' (with D.J. Littewood and B.L. Boyce)  International Workshop on Computational Mechanics of Materials,
IWCMM XXII. September 2012
    \item ``Viscoplasticity using peridynamics.''  (with S.A. Silling and W. Chen) 10th US National Congress on Computational Mechanics. July 2009.
\end{itemize}

\subsubsection*{Student Delivered}

\begin{itemize}
  \item ''Modeling of Contact and Non-Local Friction in a Peridynamic Framework.'' (with J.R.~York). 13th US National Congress on Computational Mechanics. July 2015.
  \item ``Mesh-Free Nonordinary Peridynamic Bending.'' (with J.~O'Grady). 13th US National Congress on Computational Mechanics. July 2015.
  \item ``A Peridynamic Model for Hydraulic Fracture.'' (H.~Ouichi, A.~Katiyar, M.~Sharma). 13th US National Congress on Computational Mechanics. July 2015.
  \item ``Peridynamic beams, plates, and shells: a non-ordinary state-based model.'' (with J.~O'Grady). ASME 2014 International Mechanical Engineering Congress and Exposition. November 2014.
  \item ``Peridynamic beams, plates, and shells: a non-ordinary state-based model.'' (with J.~O'Grady). Society of Engineering Science 2014. October 2014.
  \item ``The Next Generation Model for Predicting the Growth of Complex Fracture Networks.'' (with J.R.~York). 2014 Hydraulic Fracturing and Sand Control Joint Industry Program Technical Review.  April 2014.
  \item ``A peridynamic model of diffusive fluid flow through a deformable media.'' (with J.R.~York). 2013 SACNAS National Conference. October 2013.
  \item ``A complex-step method for tangent-stiffness calculation in a massively parallel computational peridynamics code.'' (with M.D.~Brothers and H.R.~Millwater). 12th US National Congress on Computational Mechanics. July 2013.
  \item ``Intragranular fracture and frictional effects in granular materials under pressure-shear loading.'' (with A.M. Peterson and T.J. Vogler) 18th Biennial Intl. Conference of the APS Topical Group on Shock Compression of Condensed Matter held in conjunction with the 24th Biennial Intl. Conference of the Intl. Association for the Advancement of High Pressure Science and Technology (AIRAPT). July 2013.
\end{itemize}

\subsection*{Invited Talks}

\begin{itemize}
    \item ``A multiphysics model for hydraulic fracture simulation.''  Eighth International Workshop Meshfree Methods for Partial Differential Equations. Universit\"{a}t Bonn, September 2015.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' Graduate Aerospace Laboratories, California Institute of Technology, January 2015.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' Institute for Computational Engineering Science, The University of Texas at Austin, October 2014.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' University of Illinos -- Urbana-Champaign, Department of Aerospace Engineering, September 2014.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' The University of Texas at Austin, Department of Engineering Mechanics, September 2014.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' ExxonMobil - Corporate Strategic Research, July 2014.
    \item ``A model for nonlocal diffusion and fluid-driven fracture.'' USACM/IUTAM Symposium on Connecting Multiscale Mechanics to Complex Material Design. Northwestern University. May 2014.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' The University of Texas at Austin, Department of Petroleum \& Geosystems Engineering. March 2014.
    \item ``Nonlocal multiphysics for heterogeneous materials, anomalous diffusion, and fracture.'' Northwestern University, Department of Mechanical Engineering. January 2014.
    \item ``Peridynamics as a unified theory for heterogenous media, anomalous porous flow, and fracture.'' The University of Texas at Austin, Department of Petroleum \& Geosystems Engineering. October 2013.
    \item ``Unifying the mechanics of continuous and discontinuous media.''  Army Research Laboratory.  February 2013.
    \item ``Unifying the mechanics of continuous and discontinuous media.''  The Johns Hopkins University, Center for Advanced Ceramics and Metallic Systems.  July 2012.
    \item ``Unifying the mechanics of continuous and discontinuous media.''  Texas Tech University, Mechanical Engineering.  April 2012.
    \item ``Hydraulic fracturing and its environmental impact: a short address of major public concerns.'' Presentation for the Center for Simulation, Visualization, and Real-Time Prediction participation in UTSA Earthweek 2012.  April 2012.
    \item ``Unifying the mechanics of continuous and discontinuous media.''  2011 International Workshop on Intensive Loading and its Effects.  State Key Laboratory of Explosion Science and Technology, Beijing Institute of Technology.  Beijing, China. December 2011.

    \item ``Peridynamic modeling of viscoplasticity and dynamic fracture.''  University of Nebraska, Engineering Mechanics. April 2010.

    \item ``Peridynamic modeling of viscoplasticity and dynamic fracture.''  University of New Mexico, Mechanical Engineering. February 2010.
\end{itemize}

\subsection*{Poster}

\begin{itemize}
  \item ``Intragranular fracture and frictional effects in granular materials under pressure-shear loading.'' (with A.M. Peterson and T.J. Vogler) 18th Biennial Intl. Conference of the APS Topical Group on Shock Compression of Condensed Matter held in conjunction with the 24th Biennial Intl. Conference of the Intl. Association for the Advancement of High Pressure Science and Technology (AIRAPT). July 2013.
\end{itemize}


