\section*{References}

\begin{itemize}

    \item Prof. Philippe Geubelle, Professor and Head \\  Department of Aerospace Engineering \\ University of Illinois at Urbana-Champaign \\ 306 Talbot Lab. \\ 104 South Wright Street \\ Urbana, IL 61801 \\ 217-244-7648 \\ \href{mailto:geubelle@illinois.edu}{geubelle@illinois.edu}

    \item Prof. K.T. Ramesh, Professor \\ Alonzo G. Decker Jr. Professor of Science \& Engineering \\ Director, Hopkins Extreme Materials Institute (HEMI) \\ Department of Mechanical Engineering \\ Johns Hopkins University \\ Latrobe 122 \\ Baltimore, MD 21218 \\ 410-516-7735 \\ \href{mailto:ramesh@jhu.edu}{ramesh@jhu.edu}

    \item Prof. Weinong (Wayne) Chen, Professor \\ Schools of Aeronautics and Astronautics and Materials Engineering \\ Purdue University\\ 3323 Neil Armstrong Hall of Engineering \\ 701 W. Stadium Ave. \\ West Lafayette, IN 47907 \\ 765-494-1788 \\ \href{mailto:wchen@purdue.edu}{wchen@purdue.edu}

    \item Dr. Michael J. Forrestal, Distinguished Member of Technical Staff ({\it retired}) \\ Sandia National Laboratories\\ 3029 Tanglewood Park West \\ Ft. Worth, TX 76109 \\ 817-914-0474 \\ \href{mailto:mjforrestal@gmail.com}{mjforrestal@gmail.com}

    \item Dr. Stewart A. Silling, Distinguished Member of Technical Staff \\ Sandia National Laboratories\\ PO Box 5800, MS 1322 \\ Albuquerque, NM 87185\\ 505-844-3973 \\ \href{mailto:sasilli@sandia.gov}{sasilli@sandia.gov}
    
    %\item Dr. Brad L. Boyce, Principal Member of Technical Staff \\ Sandia National Laboratories\\ PO Box 5800, MS 0889 \\ Albuquerque, NM 87185\\ 505-845-7525 \\ \href{mailto:blboyce@sandia.gov}{blboyce@sandia.gov}

    %\item Dr. Joseph E. Bishop, Principal Member of Technical Staff \\ Sandia National Laboratories\\ PO Box 5800, MS 0372\\ Albuquerque, NM 87185\\ 505-845-0478 \\ \href{mailto:jebisho@sandia.gov}{jebisho@sandia.gov}

  \end{itemize}

