\section*{Significant Service Activities}

\subsection*{Conferences/Workshops Organized}
  \begin{enumerate}
      \item US National Congress on Computational Mechanics 15
          \begin{itemize}
             \item {\bf Conference Chiar}
             \item \emph{To be held} in Austin, TX, July 28-August 1, 2019
          \end{itemize}
      \item Workshop on Isogeometric Analysis and Meshfree Methods
          \begin{itemize}
             \item Sponsered by the US Association for Computational Mechanics.
             \item \emph{To be held} at UCSD, October 10-12, 2016
             \item \url{http://iga-mf.usacm.org}
          \end{itemize}
      \item Workshop on Meshfree Methods for Computational Science and Engineering
          \begin{itemize}
             \item Sponsered by the US Association for Computational Mechanics.
             \item Held at UCF, October 27-28, 2014
             \item \url{http://mmlcse2014.usacm.org}
          \end{itemize}
      \item Workshop on Nonlocal Damage and Failure: Peridynamics and other nonlocal models.  
          \begin{itemize}
             \item Sponsered by the US Association for Computational Mechanics.
             \item Held at UTSA Downtown Campus, March 11-12, 2013
             \item \url{http://ndf2013.usacm.org}
          \end{itemize}
  \end{enumerate}

\subsection*{Mini-symposia Organized}

\begin{enumerate}
    \item Modeling of Material Failure Using Approaches Beyond Locality: A Celebration of Dr. Stewart Silling's 60$^{th}$ Birthday, \emph{To be held} ASME IMECE2016
    \item Corrosion Damage and Stress Corrosion Cracking: Experiments, Modeling, and Computations, ASME IMECE2015
    \item Advances in nonlocal/peridynamic modeling: Symposia in honor of Dr.~Stewart Silling's 55$^{th}$ birthday, ASME IMECE2012.
    \item Multiscale methods and nonlocal theories for complex material behavior. USACM USNCCM12.
    \item Multiscale Modeling of Dynamic Material Behavior, SEM Annual Conference 2014.
    \item Multiscale Modeling of Dynamic Material Behavior, SEM Annual Conference 2013.
    \item Multiscale Modeling of Dynamic Material Behavior, SEM Annual Conference 2012.
\end{enumerate}

\subsection*{Committee Assignments}
\subsubsection*{Department}
\begin{itemize}
    \item PGE Graduate Admissions Committee 2015-2016
    \item PGE Department Awards Committee 2014-2015
    \item Graduate Committee 2013-2014 (UTSA)
    \item Faculty Search Committee 2013-2014 (UTSA)
    \item Department Promotional Activities 2012-2013 (UTSA)
    \item Seminar 2011-2012 (UTSA)
\end{itemize}

\subsubsection*{University}
\begin{itemize}
    \item Undergraduate Research Day Planning Committee (UTSA)
\end{itemize}

\subsection*{Student Organization Advisor}
\begin{itemize}
    \item Tau Beta Pi 2013-2014 (UTSA)
    \item Formula SAE Car Team 2013-2014 (UTSA)
\end{itemize}



